PoseIntelliGraph: Detecting Violence in Video Using Human Pose Graph Neural Networks\\

### 2025-06-08 paper.tex
Feat/paper v0.1.0 (#11)
* feat: Initi paper v0.1.0

* fix: Make sure figs with the width of the page

* chore: Update v0.1.0 of paper

* chore: Update v0.1.0 of paper

* chore: Update v0.1.0 of paper

* chore: Update v0.1.0 of paper

* chore: Update v0.1.0 of paper

* chore: Update v0.1.0 of paper

* feat: Updated text in paper submission

* feat: Remove unused imports pre-commit hooks

---------

Co-authored-by: Marc <marc.reyes@angkas.com>

\section{Introduction}
The automatic detection of violent behavior in video content represents a
significant challenge in computer vision and artificial intelligence research.
With the exponential growth of video data across social media, surveillance
systems, and streaming platforms, there is an increasing need for reliable
automated methods to identify potentially harmful content
\cite{demarty2014violent}. Traditional approaches have primarily relied on
appearance-based features extracted from RGB video frames, employing
convolutional neural networks (CNNs) to classify violent actions
\cite{sudhakaran2017learning}. However, these methods often struggle with
generalization across different environments, lighting conditions, and camera
angles.

@@

Despite these advances, existing research has insufficiently explored the
integration of GNNs and Transformers for violence detection from human pose
data. Most prior work has either utilized GNNs alone \cite{yan2018spatial} or
employed more traditional sequence models such as recurrent neural networks
\cite{li2019actional}. Furthermore, many approaches have focused on simple
graph architectures that fail to fully leverage the different types of graph
convolutions available, each with their unique strengths in capturing different
aspects of graph structure.

@@

\subsection{Multi-Layer GNN Component}
Our GNN component employs three specialized layers, each addressing different
aspects of graph structure learning:

@@

We also employ JumpingKnowledge connections \cite{xu2018representation} to
preserve information from earlier layers, which helps capture multi-scale
structural patterns:

@@

To address these challenges, we employed stratified sampling during dataset
splitting and applied data augmentation techniques such as random rotation,
scaling, and flipping to pose keypoints.

>>>>

\section{Introduction}
The automatic detection of violent behavior in video content represents a
significant challenge in computer vision and artificial intelligence research.
With the exponential growth of video data across social media, surveillance
systems, and streaming platforms, there is an increasing need for reliable
automated methods to identify potentially harmful content
\cite{demarty2014violent}. Traditional approaches have primarily relied on
appearance-based features extracted from RGB video frames, using convolutional
neural networks (CNNs) to classify violent actions
\cite{sudhakaran2017learning}. However, these methods often struggle with
generalization across different environments, lighting conditions, and camera
angles.

@@

Despite these advances, existing research has insufficiently explored the
integration of GNNs and Transformers for violence detection from human pose
data. Most prior work has either utilized GNNs alone \cite{yan2018spatial} or
used more traditional sequence models such as recurrent neural networks
\cite{li2019actional}. Furthermore, many approaches have focused on simple
graph architectures that fail to fully leverage the different types of graph
convolutions available, each with their unique strengths in capturing different
aspects of graph structure.

@@

\subsection{Multi-Layer GNN Component}
Our GNN component uses three specialized layers, each addressing different
aspects of graph structure learning:

@@

We also use JumpingKnowledge connections \cite{xu2018representation} to
preserve information from earlier layers, which helps capture multi-scale
structural patterns:

@@

To address these challenges, we used stratified sampling during dataset
splitting and applied data augmentation techniques such as random rotation,
scaling, and flipping to pose keypoints.
